---
title: "class_2_27"
author: "Tommy King"
date: "2023-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
# developing for loops using a count variable to track the amount of loops 

# for the first year, must manually set it because there is no prior year. Once done, then you can loop it, starting at year 2


```

For Loop Example: Make a random sample of fertilizer application, 10 values with mean of 5 and standard deviation of 0.5. (use rnorm function to do this)

Function to compute crop yield is as follows: yield= 1.8∗fertilizer^2 − 0.5∗fertilize r+ 0.1∗TP
and TP is mean precipitation in cm


## Task 1: Use for loop to compute for total yield after 10 years
```{r}


#defining the function
fertilizer = rnorm(n = 10, mean = 5, sd=0.5)

TP = 20

# converting to data frame
crop = data.frame(fertilizer = fertilizer)
crop$yield = NA

#creating for loop for 10 values 
for(yr in 1:10){
  crop$yield[yr] = 1.8*fertilizer[yr]^2 - 0.5*fertilizer[yr] + 0.1*TP
}

sum(crop$yield)
```
## Task 2: Create a function that takes as input a single value for annual fertilizer and annual total precipitation and returns yield
```{r}

# defining function and variables -- NOTE: before a function can be run, its variables (ie: fertilizer and TP) must be defined using the function() command.

compute_yield = function(fertilizer, TP){
  yield = 1.8*fertilizer^2 - 0.5*fertilizer + 0.1*TP
  
  return(yield)
}

# applying function
compute_yield(fertilizer, TP)

sum(compute_yield(fertilizer, TP))


```
## Task 3: Modify your function so that it returns total yield if the user inputs a vector of fertilizer and a vector of precipitation
```{r}
# Now computing yield with vectors inputted for fertilizer and Total Precipitation

compute_yield(fertilizer =c(2,3,4), TP = c(10,20,30))

sum(compute_yield(fertilizer, TP))

```

