---
title: "Control Structures"
author: "Tommy King"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simple example of flow control with if 
```{r}
mycortest = function(x,y, thresh=0.8){
  #compute correlation
  res= cor(x,y)
  classification = ifelse(res > thresh, "GOOD", "NOTGOOD")
}

a = runif(min=1, max=100, n=100)
b = runif(min=1, max=100, n=100)

mycortest(a,b)
```


##Another simple example with if
```{r}

possible.fish = c("salmon", "steelhead", "shark", "tuna", "cod")
catch1= base::sample(possible.fish, size=1, replace=T)
catch1
```


##Using Case When to set conditions 
```{r}
fish = "steelhead"

case_when((fish =="steelhead")  ~ "A", (fish =="tuna") ~ "B", !(fish == "tuna") & !(fish=="steelhead") ~ "C")



# apply to all of our ocean
# start by making a function
classify_fish = function(fish) {
 class=  case_when((fish =="steelhead")  ~ "A", (fish =="tuna") ~ "B", !(fish == "tuna") & !(fish=="steelhead") ~ "C")
 return(class) }

classify_fish("steelhead")


# apply to our ocean
possible.fish = c("salmon","steelhead","shark","tuna","cod")
catch2 = base::sample(possible.fish, size=20, replace=T)
catch2


classify_fish(catch2)
```


## A more interesting example 

Montioring pollution in a lake and we want to write a function that will let us know (flag) if risk is associated with nutrient pollutoin are high, medium, or low. 

 From ecological studies, we know that:

High Risk Conditions

risk is high if water temperature is greater than a threshold for more than 5 days, and
mean nutrient concentration is greater than a high threshold

Medium Risk Conditions

Risk is medium if water temperature is greater than a threshold for more than 5 days and
mean nutrient concentration is greater than a medium threshold

Eveything else is low risk


Inputs:

nutrient concentration for at least 5 days
temperature for at least 5 days
thresholds for temperature and nutrient (with default values)

Output:

Mean Nutrient Concentration
Pollution Risk as “low”, “med” or “high”

Take a look at classify_lake

example of while
example of flow control with if..else and case_when

```{r}
read.table("fish.txt")

```

