---
title: "class_2_27"
author: "Tommy King"
date: "2023-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
# developing for loops using a count variable to track the amount of loops 

# for the first year, must manually set it because there is no prior year. Once done, then you can loop it, starting at year 2




```

For Loop Example: Make a random sample of fertilizer application, 10 values with mean of 5 and standard deviation of 0.5. (use rnorm function to do this)

Function to compute crop yield is as follows: yield= 1.8∗fertilizer^2 − 0.5∗fertilize r+ 0.1∗TP
and TP is mean precipitation in cm


## Task 1: Use for loop to compute for total yield after 10 years
```{r}


#defining the function
fertilizer = rnorm(n = 10, mean = 5, sd=0.5)

TP = 20

# converting to data frame
crop = data.frame(fertilizer = fertilizer)

#creating new column for "yield" - setting it to NA for placeholder
crop$yield = NA

#creating for loop for 10 values 
for(yr in 1:10){
  crop$yield[yr] = 1.8*fertilizer[yr]^2 - 0.5*fertilizer[yr] + 0.1*TP
}

sum(crop$yield)
```
## Task 2: Create a function that takes as input a single value for annual fertilizer and annual total precipitation and returns yield
```{r}

# defining function and variables -- NOTE: before a function can be run, its variables (ie: fertilizer and TP) must be defined using the function() command.

compute_yield = function(fertilizer, TP){
  yield = 1.8*fertilizer^2 - 0.5*fertilizer + 0.1*TP
  
  return(yield)
}

# applying function
compute_yield(fertilizer, TP)

sum(compute_yield(fertilizer, TP))


```
## Task 3: Modify your function so that it returns total yield if the user inputs a vector of fertilizer and a vector of precipitation
```{r}
# Now computing yield with vectors inputted for fertilizer and Total Precipitation

compute_yield(fertilizer =c(2,3,4), TP = c(10,20,30))

sum(compute_yield(fertilizer, TP))

```
## Error Checking: Using stop() and warning() functions to check for errors
```{r}
# stop actually stops the run, but the warning doesn't stop the run, simply provides a note that something may be awry 

```

# Class March 1st, -- Nesting For Loops 
## Example 1 - Net Present Value
```{r}
# calculate NPV for: a range of different interest rates, a range of damages, that may be incurred 10 years in the future 

# define inputs 
source("NPV.R", echo = TRUE)

#generate inputs (interest rates, damages)
damages = c(25, 50, 100)
damages

interest_rates = seq(from=0.01, to=0.04, by=0.005)
interest_rates

#define year 
year = 10

# generate a dataframe to store results
NPVs = data.frame(matrix(nrow=length(damages), ncol=length(interest_rates)))

View(NPVs)

# now use a nested for loop to populate the dataframe
for(i in 1:length(damages)){
  
  for(j in 1:length(interest_rates)){
    
    NPVs[i,j] = NPV(value= damages[i], discount = interest_rates[j], time = year)
  }
}


# now make it pretty by renaming columns and rows
colnames(NPVs) = interest_rates 
rownames(NPVs) = damages

NPVs

```


