---
title: "Class 3_8"
author: "Tommy King"
date: "2023-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(testthat)
library(tidyverse)
library(ggplot2)
library(devtools)

# notes


```
- test_dir(“name”) :runs all tests in the “name” subdirectory (all files beginning with the word “test”

 - test_file(“name”): runs all the tests in a file called “name”


Notes: 

functions that you can use to make sure your code is working the way you think it should be working

 - expect_true(condition)
 - expect_equal(value, value)
 - expect_match(string1, string2)
 - expect_null(value)
 - expect_length(object, n)
 
```{r}
# runs a test on a statement and checks to see if it is corrrect 

expect_equal(2+2, 4)

# this one should 'throw and error'

expect_equal(2+5, 4)

```
 
```{r}
# we can also use expect_true()
# works with variables too

a = 200
expect_true(a > 2)

a = 0
expect_true(a>2)

```

```{r}
# example with matches 

fish1 = "salmon"
fish2 = "trout"

expect_match(fish1, fish2)
```

```{r}
# lengths 

a = seq(from=1, to=10)

expect_length(a, 10)
expect_length(a, 11)
```


More in-depth examples using 'NPV.r'

```{r}
source("NPV.R")

# testing if future value is positive (should always be positive)

# this should work
futurevalue = 100
expect_true(NPV(value=futurevalue, time =10, discount = 0.01) >0) 

#this should give us an error
futurevalue = -100
expect_true(NPV(value=futurevalue, time =10, discount = 0.01) >0) 
```

```{r}
# what if function returns a list? 
# we can se the built in summary function to see how this works

testdata = rnorm(mean = 25, sd = 3, n=100)
summary(testdata)

# it is actually returning a list, but what are the names? 

names(summary(testdata))

# now we can specify them 
summary(testdata)["Max."]

#and use in a test to make sure this function works
expect_true(summary(testdata)["Max."]-summary(testdata)["Min."]>0)
```


Lets create a function with an error

We want a function that computes total rainfall and total recharge from a daily time series of rainfall

Daily recharge of water to soil after rain is:

recharge = daily rainfall - interception

inputs: time series of daily rainfall (mm), single value interception (default 1mm)

outputs: totalrainfall (mm), totalrecharge (mm)

```{r}
effective_rain = function(rainfall, inteception){
  
  # get total rain 
  totalrain = sum(rainfall)
  
  
}
```

